Dependent Object Types

### 2012-08-29 doc/candidacy/report.tex
minor

Scala's abstract types have close resemblances to abstract types of
signatures in these ML-like module systems. % TODO: develop

Their calculus is grounded in type theory. It is based on Girard's
$F_\omega$~\cite{tapl}. They add {\it translucent sums} to model
modules, dependent functions to model functors, a notion of subtyping
to model module implementation-interface matching. The crucial
addition and novelty is that of a {\it translucent sum}. A translucent
sum has the form of a possibly empty sequence of bindings. Similarly,
a translucent sum type has the form of a possibly empty sequence of
declarations. They differ from traditional records, because they can
contain types and because later fields can depend on ealier
ones. Translucent sums are ordinary values. Since they model modules,
it means that modules are first-class values. There's a form of
dependent type, since translucent sums are expressions that may
contain types.

@@

\subsection{A Nominal Theory of Objects with Dependent Types~\cite{nuObj}}

\subsection{Tribe: a simple virtual class calculus~\cite{tribe}}

>>>>

Their calculus is grounded in type theory. It is based on Girard's
$F_\omega$~\cite{tapl}. They add {\it translucent sums} to model
modules, dependent functions to model functors, a notion of subtyping
to model module implementation-interface matching. The crucial
addition and novelty is that of a {\it translucent sum}. A translucent
sum has the form of a possibly empty sequence of bindings. Similarly,
a translucent sum type has the form of a possibly empty sequence of
declarations. They differ from traditional records, because they can
contain types and because later fields can depend on ealier
ones. Translucent sums are ordinary values. Since they model modules,
it means that modules are first-class values.

Scala's abstract types have close resemblances to abstract types of
signatures in these ML-like module systems. In particular, in their
calculus, there's a form of dependent type, since translucent sums are
expressions that may contain types. Compared to path-dependent types
as found in Scala, these are more limited because recursive references
are not allowed.

@@

\subsection{Tribe: a simple virtual class calculus}

\subsection{A Nominal Theory of Objects with Dependent Types}
